	 vim:linebreak:nowrap:nospell tw=78 fo=tqnr foldcolumn=3 

--- 
# Spaces, no Tabs
title: Template for .Rmd 
output: 
  pdf_document: 
    latex_engine: xelatex
toc: TRUE 
toc_depth:  1 
fontsize: 12pt 
geometry: margin=0.5in,top=0.25in 

---
/home/jim/.config/nvim/templates/skeleton.Rmd
othercomments
---

<!--  commments -->

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,  
											comment="      ##",  
											error=TRUE, 
											collapse=TRUE) 
```

```{r library, include=FALSE		}
library(jimTools) 
load_all()
``` 

```{r render, eval=FALSE	} 
file <- "" 
file  <- basename(file) 
dir <-"rmd"

jimTools::ren_pdf(file,dir)
jimTools::ren_github(file, dir)
```

```{r begin}


# set in .Rprofile
set_os_key(Sys.getenv("API_KEY"))

t  <- get_legislators( state="OR",
									api_key = get_os_key())	

```

```{r examine_candidates}
names(t)

# 1st name, Bonamici cid =?
t$cid[[1]]

# SAME
purrr::pluck(t,"cid", 1)

```

***

```{r knit_exit()} 
knitr::knit_exit() 
```


Parameters
apikey:	(required) Your API Key
id:	(required) two character state code or specific CID
output:	(optional) Output format, either json, xml, or doc; default is xml
Example Call
http://www.opensecrets.org/api/?method=getLegislators&id=NJ&apikey=__apikey__
Response Details



