---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# opensecrets

<!-- badges: start -->
<!-- badges: end -->

The goal of opensecrets is to create a reimagining of the OpenSecrets API. The package is intended to follow almost verbatim with the [API documentation](https://www.opensecrets.org/open-data/api-documentation). Refer to the documentation for more information of the data that is retrieved.

## Installation

You can install the released version of opensecrets from [GitHub](https://github.com/josiahparry/opensecrets) with:

```{r eval=FALSE}
remotes::install_github("josiahparry/opensecrets")
```


This package is in very experimental phases and is subject to breaking. There is much to do, but a this serves as a minimal viable product.

Please submit issues and feature requests as you come about them.

## API Key

Register with OpenSecrets and register for an API key at [this link](https://www.opensecrets.org/api/admin).

Set your key using `set_os_key("my_key_here")` or store it in `.Renviron`



## Examples

List all available legislators for a given state.

```{r}
library(opensecrets)

ca_legislators <- get_legislators("CA")
ca_legislators
```

Get personal finance information for a given legislator.

```{r message=FALSE, warning=FALSE}
library(tidyverse)

# get Nancy Pelosi
ca_legislators %>% 
  filter(firstlast == "Nancy Pelosi") %>% 
  pull(cid) %>% 
  personal_finance()
```

Use `purrr::map()` to iterate over multiple individuals.

```{r message=FALSE, warning=FALSE}
ca_legislators %>% 
  # take only 3 legislators
  slice(1:3) %>% 
  mutate(pf = map(cid, personal_finance)) %>% 
  unnest()
```

